% ============================================================
% COVER LETTER
% ============================================================
\newdocument{Cover Letter}

\applicantblock

\vspace{0.5em}
\noindent\textbf{Date:} \SubmissionDate

\vspace{1em}
\agencyblock

\sectionrule

\reline{Criminal Record Exemption Request --- \CertificationType\ Application}
\noindent\textbf{Applicant Name:} \ApplicantName\\
\textbf{Facility Type:} \FacilityType

\sectionrule

\vspace{0.5em}
Dear \BranchAbbrev\ Exemption Review Team,

I am writing in response to the Exemption Needed --- Initial Applicant notice I received from the \BranchFull\ regarding my application for \CertificationType. I understand that my criminal record contains information that requires an exemption, and I am submitting this complete packet to satisfy the requirements outlined in your notice.

I accept full responsibility for the two misdemeanor DUI convictions identified on my record (\IncidentOneDate\ and \IncidentTwoDate). Neither incident involved injuries, property damage, or accidents, and I received no jail time for either offense. Since the date of my last incident, I have dedicated myself to comprehensive rehabilitation, personal transformation, and a career pivot into eldercare and nursing.

I respectfully submit the following enclosed documents for your review:

\begin{enclosurelist}
  \item \textbf{Written Statement of Rehabilitation} --- A detailed narrative addressing the circumstances of each incident, all rehabilitation steps undertaken (both court-ordered and voluntary), my current professional and educational status, and my vision for service to the elderly population.

  \item \textbf{Proof of Completion --- DUI Program (Incident~1)} --- Certificate of completion from \DUIProgramOne\ (\DUIProgramOneDuration\ program).

  \item \textbf{Proof of Completion --- DUI Program (Incident~2)} --- Certificate of completion from \DUIProgramTwo\ (\DUIProgramTwoDuration\ program).

  \item \textbf{Proof of Completion --- Voluntary Rehabilitation Program} --- Documentation from \RehabProgram\ (\RehabDuration\ program).

  \item \textbf{Proof of Completion --- Voluntary Alcohol Monitoring} --- Documentation from \SCRAMProgramShort\ (\SCRAMDuration\ of continuous transdermal alcohol monitoring).

  \item \textbf{Proof of Completion --- Alternative Custody Program} --- Documentation from \CPACProgram, administered by the \CPACAdmin\ (\CPACDuration\ program).

  \item \textbf{Proof of AA Meeting Attendance} --- Records of Alcoholics Anonymous attendance for both incidents.

  \item \textbf{Proof of Court Compliance} --- Documentation confirming payment of all court-ordered fines, fees, and charges, as well as full compliance with all legal requirements for both cases.

  \item \textbf{Three (3) Signed Character Reference Statements (Form LIC 301E):}
  \begin{itemize}[leftmargin=1.5em, itemsep=0.15em]
    \item Reference A: \RefAName\ --- \RefATitle, \RefAOrg
    \item Reference B: \RefBName\ --- \RefBTitle
    \item Reference C: \RefCName\ --- \RefCTitle
  \end{itemize}

  \item \textbf{Supporting Professional \& Educational Documentation} \textit{(recommended):}
  \begin{itemize}[leftmargin=1.5em, itemsep=0.15em]
    \item \RCFETraining\ certificate
    \item \LLCName\ business registration (\LLCDate)
    \item \placeholder{Any additional certificates or documentation}
  \end{itemize}
\end{enclosurelist}

\vspace{0.5em}
I have made every effort to be thorough, transparent, and forthcoming in this submission. I welcome any questions the review team may have and am fully available for an interview, additional documentation requests, or any other steps required to complete this process.

I am deeply committed to the caregiving profession and to demonstrating that I have been fundamentally changed by my rehabilitation journey. I respectfully ask the Department to consider the totality of my circumstances, including the proactive steps I have taken far beyond court requirements, my stable professional history, and my clear trajectory toward becoming a licensed healthcare professional dedicated to serving California's elderly population.

Thank you for your time and careful consideration of my application.

\vspace{1em}
\noindent Respectfully submitted,

\signatureline{\ApplicantName}
\datefield

\vspace{1em}
{\small\textit{This letter and all enclosed documents are also being uploaded through the Guardian portal at \url{\GuardianPortal}.}}
