% ============================================================
% CHARACTER REFERENCE A — Owner / Executive (Uni Care, Inc.)
% Form LIC 301E
% Perspective: Senior organizational leadership — strategic,
% top-down view of character, trust, and professional reliability.
% ============================================================
\newdocument{Character Reference --- Owner/Executive}
\resetlicquestions

\licformheader

\licwriterinfo
  {\RefAName}
  {\RefAAddress}
  {\RefACityStateZip}
  {\RefAPhone}

% ----------------------------------------------------------
\licquestion{How long have you known the person you are writing this reference for?}

I have known \ApplicantName\ for \RefAKnownDuration, since he joined \EmployerName\ in \RefAKnownSince. Throughout this period, in my capacity as \RefATitle\ of the organization, I have had continuous and direct visibility into his professional conduct, judgment, and character, both in day-to-day operations and during moments that test a person's integrity.

% ----------------------------------------------------------
\licquestion{How do you know this person?}

\ApplicantName\ serves as the \EmployerRole\ at \EmployerName, the parent organization of \EmployerDivisions. In this role, he is responsible for the enterprise-wide technology infrastructure that supports our clinical and administrative operations---including HIPAA-compliant electronic health record systems, secure communications for over \TeamSize\ staff members, telehealth and remote monitoring platforms, and the network and cybersecurity posture of our entire organization. Because our operations serve elderly and medically vulnerable populations in their homes across multiple counties, the integrity of these systems is directly tied to patient safety. As a senior leader of this organization, I rely on \ApplicantName\ to make sound decisions that protect both our patients and our staff, and I have engaged with him regularly on strategic, operational, and compliance matters throughout his tenure.

% ----------------------------------------------------------
\licquestion{Please give your opinion of this person's character.}

\ApplicantName\ is among the most trustworthy, disciplined, and principled professionals I have employed during my career in healthcare leadership. He is a person of integrity who consistently chooses transparency over self-protection, accountability over excuse-making, and long-term responsibility over short-term convenience. He is respected by staff at every level of the organization and has earned the trust of our executive team through years of demonstrated reliability.

I am fully and specifically aware that \ApplicantName\ has two misdemeanor DUI convictions on his record---one from \IncidentOneDate\ and one from \IncidentTwoDate. \ApplicantName\ disclosed this to me personally and voluntarily. He did not wait for the information to surface; he brought it forward himself, directly, with complete candor about the circumstances and with a clear account of the steps he was taking to address the underlying issues. In my professional experience, an individual's willingness to disclose difficult information about themselves---when they could have chosen not to---is one of the most reliable indicators of character.

What I have witnessed in the time since has only strengthened my confidence. \ApplicantName\ did not settle for completing the court-mandated programs. He voluntarily enrolled in an intensive, long-term rehabilitation program at \RehabProgram\ for \RehabDuration---at his own initiative, on his own time, and at his own expense. He has consistently maintained his professional responsibilities, met every deadline, and delivered his work with the same rigor that has defined his tenure. I have observed a measurable deepening of his self-awareness, discipline, and emotional maturity. He is, by every meaningful measure, a better version of the professional I hired in \EmployerSince.

I trust him without qualification.

% ----------------------------------------------------------
\licquestion{Please describe any interaction you have observed between this person and the client group he/she is requesting to work with. For example: Clients may be children, developmentally disabled children or adults, mentally impaired adults, or elderly.}

\EmployerName\ exists for the care of vulnerable populations---primarily elderly patients receiving home health services, hospice care, and personal care assistance. Although \ApplicantName's formal role is in IT management, his work places him in continuous, meaningful contact with the caregiving environment, and I have observed his conduct in this environment on many occasions:

\begin{itemize}[leftmargin=2em, itemsep=0.2em]
  \item I have accompanied \ApplicantName\ on organizational site visits where elderly patients were present, and I have observed him conduct himself with quiet professionalism, discretion, and genuine respect for patient dignity and privacy.
  \item In executive reviews of patient satisfaction data, clinical outcomes, and technology-enabled care initiatives, \ApplicantName\ consistently frames his work around the question of how our systems ultimately serve the elderly patients we exist to care for---not as a talking point, but as a genuine operating principle.
  \item When our clinical teams have encountered technology failures in the field---at a patient's bedside, during a hospice transition, or in a moment of clinical urgency---\ApplicantName\ has responded with a sense of mission, recognizing that his rapid resolution of an IT issue is often the difference between uninterrupted care and a preventable disruption for a vulnerable patient.
  \item At company events that have included patients and family members, I have observed him interact with elderly individuals with warmth, patience, and the kind of unhurried attention that is rare and meaningful.
\end{itemize}

His commitment to residential care administration is a natural extension of the character and service orientation I have observed in him every day at \EmployerName.

% ----------------------------------------------------------
\licquestion{Please add any comments you feel are relevant about this person and his/her desire to work in a community care facility.}

I want to convey several points that I believe are directly relevant to the Department's evaluation:

\textbf{Full Awareness and Unqualified Support:} I am fully aware of both DUI misdemeanor convictions on \ApplicantName's record and the circumstances surrounding each. This knowledge has not reduced my confidence in him---it has deepened it. Watching a professional respond to serious personal failure with total accountability, proactive clinical treatment, sustained behavioral change, and unwavering professional performance is rare, and it reveals character in a way that unblemished records cannot.

\textbf{Professional Trust at the Highest Level:} Over \RefAKnownDuration, \ApplicantName\ has been entrusted with our most sensitive operational, financial, clinical, and patient-privacy systems. He has never betrayed that trust, and his standing within the organization today is stronger than it has ever been. The fact that he continues to hold this level of responsibility---including through the periods of both incidents---reflects the consistent confidence of our executive team.

\textbf{Relevant Qualifications for RCFE Administration:} \ApplicantName\ brings an unusually well-matched set of qualifications to \FacilityTypeShort\ administration. He has spent over five years managing regulatory-compliance-intensive technology operations for a California-licensed healthcare organization. He has completed the \RCFETraining. He holds \EducationDegrees, which reflect a proven capacity for complex systems, rigorous documentation, and sustained academic discipline---the same competencies that define effective facility administration under Title 22 and Community Care Licensing oversight.

\textbf{A Person the Department Can Trust:} I understand that the Department's obligation is to protect elderly Californians from individuals who lack the character to serve them safely. With full knowledge of \ApplicantName's record, I can state without hesitation that he is exactly the kind of individual the Department should want in this role: transparent, accountable, clinically rehabilitated, professionally stable, and genuinely motivated by service.

I strongly and unequivocally recommend \ApplicantName\ for the criminal record exemption and for \FacilityTypeShort\ Administrator Certification.

\licsignatureblock
