% ============================================================
% CHARACTER REFERENCE C — Community Contact
% Form LIC 301E
% ============================================================
\newdocument{Character Reference --- Community Contact}
\resetlicquestions

\licformheader

\licwriterinfo
  {\RefCName}
  {\RefCAddress}
  {\RefCCityStateZip}
  {\RefCPhone}

% ----------------------------------------------------------
\licquestion{How long have you known the person you are writing this reference for?}

I have known \ApplicantName\ for \RefCKnownDuration, since \RefCKnownSince. Over this time, I have had regular and meaningful interactions with him and have developed a thorough understanding of his character, values, and personal trajectory.

% ----------------------------------------------------------
\licquestion{How do you know this person?}

% >>> INSTRUCTIONS: Choose and personalize ONE of the options below,
% >>> then delete the others. Remove the comment markers (%) from your choice. <<<

% --- Option A: CNA Program Classmate/Instructor ---
%I know \ApplicantName\ through our shared enrollment in a Certified Nursing Assistant (CNA) training program. As classmates in the clinical and didactic portions of the program, I have observed his dedication to learning caregiving skills, his respectful interactions with instructors and fellow students, and his genuine motivation to serve elderly and vulnerable populations.

% --- Option B: Community / Neighborhood Contact ---
%I know \ApplicantName\ through our community in \placeholder{City/Neighborhood}. We have been neighbors and acquaintances for \RefCKnownDuration, and I have observed his conduct, character, and personal growth through regular interaction. I am also aware of his professional background in IT and his recent transition into the healthcare and caregiving field.

% --- Option C: Professional Network / Mentor ---
%I know \ApplicantName\ through a professional mentorship relationship. I have served as his mentor and have had in-depth conversations about his career goals, his personal challenges, and his commitment to building a meaningful career in eldercare.

% --- Option D: Faith / Community Organization ---
%I know \ApplicantName\ through our shared involvement in \placeholder{community organization / faith community / volunteer group}. Through this connection, I have observed his character, his willingness to serve others, and his genuine commitment to personal growth and accountability.

% >>> DEFAULT (remove this and uncomment your choice above): <<<
I know \ApplicantName\ through \placeholder{describe specific relationship context --- e.g., CNA program, community, mentorship, etc.}. Through this connection, I have had consistent opportunities to observe his character, dedication, and personal development over a meaningful period of time.

% ----------------------------------------------------------
\licquestion{Please give your opinion of this person's character.}

I hold \ApplicantName\ in high regard and consider him a person of genuine integrity, resilience, and moral seriousness. In every interaction I have had with him, he has demonstrated honesty, reliability, and a deep commitment to improving himself and contributing positively to his community.

I am aware that \ApplicantName\ has two misdemeanor DUI convictions on his record---one from \IncidentOneDate\ and one from \IncidentTwoDate. He shared this information with me voluntarily and openly, without prompting or obligation. I want to state unequivocally that this knowledge has not diminished my opinion of his character. If anything, it has increased my respect for him, because of the way he has responded to these challenges.

Rather than minimizing his mistakes or hiding from his past, \ApplicantName\ has confronted his history with total accountability. He voluntarily completed a long-term rehabilitation program at \RehabProgram---\RehabDuration\ of intensive therapeutic work that was not required by any court. He has attended AA meetings, completed all court-ordered programs, and made fundamental changes to his lifestyle, including committing to physical fitness, healthy habits, and disciplined daily routines. The person I know today is someone who has taken full ownership of his past and has built a life defined by purpose, service, and responsibility.

I trust \ApplicantName\ completely, and I believe he possesses the character necessary to care for and protect elderly individuals in a community care setting.

% ----------------------------------------------------------
\licquestion{Please describe any interaction you have observed between this person and the client group he/she is requesting to work with. For example: Clients may be children, developmentally disabled children or adults, mentally impaired adults, or elderly.}

% >>> INSTRUCTIONS: Choose and personalize ONE of the options below,
% >>> then delete the others. Remove the comment markers (%) from your choice. <<<

% --- Option A: CNA classmate/instructor perspective ---
%During our CNA training program, I have directly observed \ApplicantName's interactions with elderly patients and simulated care scenarios. He approaches each patient---whether in clinical rotations or lab practice---with patience, gentleness, and genuine respect for their dignity. He is attentive to each individual's needs, communicates clearly and kindly, and demonstrates the type of compassionate presence that residents of a care facility deserve. He takes his clinical responsibilities seriously and is meticulous about following proper protocols for hygiene, safety, transfers, and activities of daily living.

% --- Option B: Community/neighborhood perspective ---
%While I have not observed \ApplicantName\ in a formal clinical setting, I have seen his character and compassion demonstrated consistently in our community. He is thoughtful, respectful, and attentive in his interactions with people of all ages, including elderly neighbors and community members. He has spoken with me at length about his desire to care for the elderly and has described his experiences at \EmployerName---a home health and hospice organization---where he has been immersed in a caregiving environment for over five years. His sincerity and depth of commitment to this population are evident in every conversation.

% --- Option C: Mentor/professional perspective ---
%Through our mentorship relationship, \ApplicantName\ has shared extensively about his experiences working in a healthcare environment at \EmployerName\ and his growing passion for direct eldercare. I have observed his thoughtfulness, empathy, and genuine concern for the well-being of vulnerable populations. He approaches the caregiving profession not as a career of convenience, but as a calling rooted in personal experience and a desire to give back to his community.

% >>> DEFAULT (remove this and uncomment your choice above): <<<
Through my relationship with \ApplicantName, I have observed his genuine compassion and respect in interactions with people of all ages and backgrounds. He has spoken extensively about his desire to serve the elderly population and has described his immersion in a healthcare environment at \EmployerName\ for over five years. His sincerity, empathy, and commitment to this population are evident in every conversation and interaction.

% ----------------------------------------------------------
\licquestion{Please add any comments you feel are relevant about this person and his/her desire to work in a community care facility.}

I want to offer the following observations that I believe are important for the Department's consideration:

\textbf{Genuine Transformation:} I have known \ApplicantName\ during a period of significant personal growth, and the transformation I have witnessed is real and substantive. This is not someone who is going through the motions of rehabilitation to satisfy a requirement---this is someone who has fundamentally changed how he lives, works, and relates to others. The discipline, humility, and self-awareness he demonstrates daily are evidence of a person who has done deep, honest work on himself.

\textbf{Intentional Career Choice:} \ApplicantName's decision to pursue \FacilityTypeShort\ administration and nursing is not impulsive or opportunistic. He has invested years of preparation---completing his \RCFETraining, enrolling in a CNA program, planning for nursing school at \NursingSchool, and gaining experience in a healthcare organization. He has built the credentials, knowledge, and clinical skills necessary to serve the elderly competently and compassionately.

\textbf{Full Disclosure:} The fact that \ApplicantName\ shared his criminal history with me---voluntarily and openly---speaks volumes about his character. He is not a person who hides from his past. He understands that trust is built through transparency, and he has consistently demonstrated that principle in our relationship.

\textbf{Community Asset:} I believe \ApplicantName\ will be a genuine asset to California's community care system. His combination of technical expertise, clinical training, personal resilience, and deeply motivated commitment to service is rare. The elderly residents who will eventually be in his care will be well served by an administrator who brings not only competence but also the hard-earned wisdom and empathy of someone who has overcome personal adversity.

I wholeheartedly recommend \ApplicantName\ for the criminal record exemption and for his pursuit of \FacilityTypeShort\ Administrator Certification. I am confident he will honor the trust placed in him.

\licsignatureblock
