% ============================================================
% WRITTEN STATEMENT OF REHABILITATION — Sections I & II
% ============================================================
\newdocument{Written Statement of Rehabilitation}

\documenttitle{Written Statement of Rehabilitation}

\statementmeta

% ============================================================
\section{Personal Accountability \& Full Disclosure}
% ============================================================

I, \ApplicantName, submit this written statement in connection with my application for \CertificationType\ and the criminal record exemption process administered by the \AgencyFull\ (\AgencyAbbrev), \BranchFull\ (\BranchAbbrev). I have been informed that the Department of Justice has identified two misdemeanor convictions on my criminal record, and I am required to provide a full written explanation, evidence of rehabilitation, and character references to obtain an exemption.

I accept complete, unconditional responsibility for both incidents described below. At no point in this statement do I seek to minimize, deflect, or justify my actions. Both decisions to drive under the influence were serious lapses in judgment that I own entirely. I understand the gravity of these offenses---not only in terms of the law, but in terms of the potential harm I could have caused to other individuals, families, and communities. I am profoundly grateful that neither incident resulted in injuries, property damage, or accidents, but I do not take that outcome as a reason to diminish the seriousness of my conduct.

What I can attest to---and what I will demonstrate throughout this statement---is that these experiences became the most significant turning point of my adult life. They forced me to confront deeply rooted patterns in how I managed stress, navigated personal challenges, and coped with the pressures of building a career and life in a new country. The person submitting this application today is fundamentally different from the person who made those decisions, and I will present the clinical, professional, and personal evidence to substantiate that claim.

I have chosen to be fully transparent with my professional network about my history. The three character references accompanying this application---including the owner of \EmployerName, where I have been employed since \EmployerSince---are each fully aware of both DUI convictions and have chosen to vouch for my character, integrity, and fitness to serve the elderly population of California.

% ============================================================
\section{Circumstances of Incident One --- \IncidentOneDate}
% ============================================================

On \IncidentOneDate, I was arrested for Driving Under the Influence (DUI), which was subsequently classified as a misdemeanor. There were no injuries to any person, no property damage, and no accident associated with this incident. I did not receive jail time.

At the time, I had been living in California for approximately two years, having relocated in \EmployerSince---during the height of the COVID-19 pandemic. I was working full-time as \EmployerRole\ at \EmployerName, managing technology infrastructure across multiple divisions (\EmployerDivisions). While the demands of this role were significant---coordinating with over \TeamSize\ employees, maintaining HIPAA-compliant systems, and supporting clinical operations remotely during a pandemic---I state these facts only as context, not as justification. The decision to drive after consuming alcohol was mine alone, and no external circumstance excuses it.

\subsubsection{Immediate Actions Following Incident One}

Upon receiving the charge, I took the following steps without delay:

\begin{itemize}[leftmargin=2em, itemsep=0.2em]
  \item Retained legal counsel and cooperated fully with the court process
  \item Paid all court-ordered fines, fees, and associated charges in full and on time
  \item Enrolled in and successfully completed a \textbf{\DUIProgramOneDuration\ DUI education program at \DUIProgramOne}
  \item Began attending \textbf{Alcoholics Anonymous (AA) meetings} voluntarily and as part of my court requirements
  \item Complied with all DMV requirements including any license restrictions
  \item Maintained full compliance with every condition of my sentence
\end{itemize}

I believed at the time that I had learned from this mistake. I completed the required program, attended AA, and resumed my professional and personal life. However, as the second incident demonstrates, the first experience---while impactful---did not result in the depth of self-examination and behavioral change that was truly necessary. I am candid about this because I believe the auditor reviewing this application deserves to understand my honest self-assessment, not a polished narrative that obscures the truth.
